\tool: A Multi-Mode BadUSB Device

### 2021-01-08 WOOT/Files/related_work.tex
delete one problematic citation , probably due to the url

IMonitor EAM\cite{IMonitor} maintain a whitelist of USB devices, only if one USB device is in the whitelist can it interact with host. This prevents all interactions between untrusted devices and the host. But this reduces the ease of use and requires users to have a certain safety awareness. For example, a naive user may add the USB device he found outdoors to his whitelist without precautions.

>>>>

IMonitor EAM\cite{IMonitor}\hongyi{Citation has compilation problem, plz recheck} maintain a whitelist of USB devices, only if one USB device is in the whitelist can it interact with host. This prevents all interactions between untrusted devices and the host. But this reduces the ease of use and requires users to have a certain safety awareness. For example, a naive user may add the USB device he found outdoors to his whitelist without precautions.
